---
title: "SRO using entire data frame"
author: "Kim"
date: "5/28/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First load in the necessary packages
```{r}
library(tidyverse)
library(ggplot2)
library(caret)
library(MASS)
```
```{r}

forOSF <- read.csv("s:/ecg-members/Gliebe/Data/SRO/CombineRun20190715.115618MovieInt.csv")
head(forOSF)
```

Read in your csv file that contains the lengths, widths, and intensities of all
of your samples. When this file is saved, a "X" may be added to number the 
rows.  We remove this as to not affect the results.
```{r}

SRO <- read.csv("s:/ecg-members/Gliebe/Data/allSRO.csv")
table(SRO$sample)
SRO <- SRO %>%
  dplyr::select(-X)
head(SRO)
```

Below we are normalizing the data. You can choose what parameters to have
normalized.  These are listed above the comment line that says "list parameters
for normalization above"
```{r}
matTable <- SRO %>%
  dplyr::select(sample, mat) %>%
  dplyr::distinct()

library(caret)
data4 <- data.frame()
for (i in 2:dim(matTable)[1]) {
  #i <- 1
  samplename <- as.character(matTable$sample[i])
  dataNorm <- SRO %>% 
    dplyr::filter(sample == samplename) #%>%
  dataNorm <- dataNorm %>%
    dplyr::select(frame, Xwidth, widthsy)
  #list parameters for normalization above
  procData <- preProcess(dataNorm, method = "range")
  dataNorm <- predict(procData, dataNorm)
  data2 <- SRO %>%
    filter(sample == matTable[i,1]) %>%
    dplyr::select(-frame, -Xwidth, -widthsy)
  data3 <- cbind(data2, dataNorm)
  #data4 <- data3
  data4 <- rbind(data4, data3)
}

summary(data4)


```

Now all the data is normalized, let's split it into testing and training (without needing to keep frames of the same samples together).

```{r}
library(rsample)
set.seed(13)
split <- initial_split(data4, .6)
train <- training(split)
test <- testing(split)
#write.csv(train, "s:/ecg-members/Gliebe/Data/SROtrainFullDataNorm.csv")
#write.csv(test, "s:/ecg-members/Gliebe/Data/SROtestFullDataNorm.csv")
```

Linear Discriminant Analysis (LDA):

```{r}
test <- read.csv("s:/ecg-members/Gliebe/Data/dftesttime1trial20200505SROnormFrame.csv")
train <- read.csv("s:/ecg-members/Gliebe/Data/dftraintime1trial20200505SROnormFrame.csv")
test <- test %>% dplyr::select(-X)
train <- train %>% dplyr::select(-X)
library(MASS)
#str(train)  #result is a factor already
dfModelTrain <- train %>%
  dplyr::select(-sample) 
set.seed(4)
lda.fitmaxLtrain = lda(result∼intercept+ns1+ns2+ns3+ns4 , data = dfModelTrain)
#saveRDS(lda.fitmaxLtrain, "../Data/RawNormalizedSRO/ldaModel.rds")
predictedLDA <- predict(lda.fitmaxLtrain, dfModelTrain, type = "class")
dfModelTrain$answer <- predictedLDA$class
confTrain <- confusionMatrix(as.factor(dfModelTrain$answer), as.factor(dfModelTrain$result))
print(confTrain)
dftestModel <- test %>%
  dplyr::select(-sample)
predictedTestLDA <- predict(lda.fitmaxLtrain, dftestModel, type = "class")
dftestModel$answer <- predictedTestLDA$class
confTest <- confusionMatrix(as.factor(dftestModel$answer), as.factor(dftestModel$result))
print(confTest)
#summary(lda.fitmaxLtrain)
#lda.fitmaxLtrain
#plot(lda.fitmaxLtrain)
```


Support vector machine (SVM):
```{r}
library(e1071)

dftrainFrame <- train %>%
  dplyr::select(-sample)
dftrainFrame$result <- as.character(dftrainFrame$result)
dftrainFrame$result[dftrainFrame$result == "yes"] <- 1.0
dftrainFrame$result[dftrainFrame$result == "no"] <- 2.0

set.seed(5)
svm.fitframetrain = svm(as.factor(result)~intercept+ns1+ns2+ns3+ns4 , data = dftrainFrame)
#saveRDS(svm.fitframetrain, "../Data/RawNormalizedSRO/svmModel.rds")

predictedsvmtrainFrame <- predict(svm.fitframetrain, dftrainFrame)
dftrainFrame$answer <- predictedsvmtrainFrame

confusionMatrix(as.factor(dftrainFrame$answer), as.factor(dftrainFrame$result))

dftestFrameModel <- test  %>%
  dplyr::select(-sample)
dftestFrameModel$result <- as.character(dftestFrameModel$result)
dftestFrameModel$result[dftestFrameModel$result == "yes"] <- 1
dftestFrameModel$result[dftestFrameModel$result == "no"] <- 2

dftestFrameModel$result <- as.factor(dftestFrameModel$result)
predictedTestframeSVM <- predict(svm.fitframetrain, dftestFrameModel)
dftestFrameModel$answer <- predictedTestframeSVM
confusionMatrix(as.factor(dftestFrameModel$answer), as.factor(dftestFrameModel$result))
svm.fitframetrain
plot(svm.fitframetrain)
```

Quadratic discriminant analysis (QDA):
```{r}

dftrainFrame <- train %>%
  dplyr::select(-sample, -X)
dftrainFrame$intercept <- as.numeric(dftrainFrame$intercept)
dftrainFrame$ns1 <- as.numeric(dftrainFrame$ns1)
dftrainFrame$ns2 <- as.numeric(dftrainFrame$ns2)
dftrainFrame$ns3 <- as.numeric(dftrainFrame$ns3)
dftrainFrame$ns4 <- as.numeric(dftrainFrame$ns4)
dftrainFrame$ns5 <- as.numeric(dftrainFrame$ns5)
dftrainFrame$result <- as.numeric(dftrainFrame$result)
set.seed(5)
qda.fit=qda(result∼intercept+ns1+ns2+ns3+ns4 ,data=dftrainFrame)
#qda.fit=qda(as.numeric(result) ~ ., data = dftrainFrame)
 qda.fit

```


```{r}
library(MASS)
test <- read.csv("s:/ecg-members/Gliebe/Data/dftesttime1trial20200505SROnormFrame.csv")
train <- read.csv("s:/ecg-members/Gliebe/Data/dftraintime1trial20200505SROnormFrame.csv")
dftrainFrame <- train %>%
  dplyr::select(-sample, -X)
dftrainFrame$result <- as.character(dftrainFrame$result)
dftrainFrame$result[dftrainFrame$result == "yes"] <- 1
dftrainFrame$result[dftrainFrame$result == "no"] <- 2
dftrainFrame$result <- as.numeric(dftrainFrame$result)
#str(dftrainFrame)
#summary(dftrainFrame)
set.seed(4)
qda.fitmaxLtrain = qda(result∼intercept+ns1+ns2+ns3+ns4 ,data=dftrainFrame)
#saveRDS(qda.fitmaxLtrain, "../Data/RawNormalizedSRO/qdaModel.rds")
predictedQDA <- predict(qda.fitmaxLtrain, dftrainFrame, type = "class")
dftrainFrame$answerQDA <- predictedQDA$class
#dfmaxLtest$rfmaxL <- as.factor(predictedrfmaxL)
confusionMatrix(as.factor(dftrainFrame$answerQDA), as.factor(dftrainFrame$result))

dftestFrame <- test %>%
  dplyr::select(-sample, -X)
dftestFrame$result <- as.character(dftestFrame$result)
dftestFrame$result[dftestFrame$result == "yes"] <- 1
dftestFrame$result[dftestFrame$result == "no"] <- 2
dftestFrame$result <- as.numeric(dftestFrame$result)
predictedQDA <- predict(qda.fitmaxLtrain, dftestFrame, type = "class")
dftestFrame$answerQDA <- predictedQDA$class
confusionMatrix(as.factor(dftestFrame$answerQDA), as.factor(dftestFrame$result))
qda.fitmaxLtrain
plot(qda.fitmaxLtrain)
```


log mod:
```{r}
test <- read.csv("s:/ecg-members/Gliebe/Data/dftesttime1trial20200505SROnormFrame.csv")
train <- read.csv("s:/ecg-members/Gliebe/Data/dftraintime1trial20200505SROnormFrame.csv")
dftrainFrame <- train %>%
  dplyr::select(-sample, -X)
dftrainFrame$result <- as.factor(dftrainFrame$result)
dftestFrame <- test %>%
  dplyr::select(-sample, -X)
dftestFrame$result <- as.factor(dftestFrame$result)
set.seed(3)
logMod <- glm(result∼intercept+ns1+ns2+ns3+ns4 , data = dftrainFrame, family = binomial)
#saveRDS(logMod, "../Data/RawNormalizedSRO/logModel.rds")
glm.probs <- predict(logMod, type = "response")
glm.pred = rep("no", 13)
glm.pred[glm.probs > .5] = "yes"
glm.pred <- as.factor(glm.pred)
confusionMatrix(glm.pred, dftrainFrame$result)
glm.pred
glm.probs <- predict(logMod, dftestFrame)
glm.pred = rep("no", 14)
glm.pred[glm.probs > .5] = "yes"
glm.pred <- as.factor(glm.pred)
confusionMatrix(glm.pred, dftestFrame$result)
logMod
```



```{r}
library(leaps)
dftrainFrame <- train %>%
  dplyr::select(-sample, -X)
dftrainFrame$result <- as.numeric(dftrainFrame$result)
dftestFrame <- test %>%
  dplyr::select(-sample, -X)
dftestFrame$result <- as.factor(dftestFrame$result)
set.seed(3)
subMod <- regsubsets(result ~ . , data = dftrainFrame)
summary(subMod)
#saveRDS(logMod, "../Data/RawNormalizedSRO/logModel.rds")
linMod <- lm(result ~ . , data = dftrainFrame)
lm.probs <- predict(linMod, dftrainFrame)
lm.pred = rep(1, 21156)
lm.pred[lm.probs > 1.5] = 2
confusionMatrix(as.factor(lm.pred), as.factor(dftrainFrame$result))

```


Let's do some eda to see what's happening

```{r}
#str(train)
yes <- train %>%
  dplyr::filter(result == "yes")
ggplot(data = yes, aes(x = Xwidth, fill = as.factor(peakNum))) +
  geom_histogram(position = "dodge")

no <- train %>%
  dplyr::filter(result == "no")
ggplot(data = no, aes(x = Xwidth, fill = as.factor(peakNum))) +
  geom_histogram(position = "dodge")

```


```{r}
#str(train)
yes <- train %>%
  dplyr::filter(result == "yes")
ggplot(data = yes, aes(x = widthsy, fill = as.factor(peakNum))) +
  geom_histogram(position = "dodge")

no <- train %>%
  dplyr::filter(result == "no")
ggplot(data = no, aes(x = widthsy, fill = as.factor(peakNum))) +
  geom_histogram(position = "dodge")

```


```{r}
library(klaR)
partimat(as.factor(result) ~ ., data = dftrainFrame, method = "qda", plot.matrix = TRUE, col.correct='green', col.wrong='red')

#str(dftrainFrame)
```














